### 2017-01-27 manuscript.rmd
Update manuscript.rmd

Most CFG studies to date compare gene expression across species, often between distinct tissues or developmental time points. Gene expression has been a popular target of CFG studies because, with the advent of RNA-Seq and related transcriptome sequencing methods, it is the most readily collected functional genomics trait across diverse species. Here we reconsider two recent comparative analyses of gene expression data [@KryuchkovaMostacci:2016iw; @Levin:2016bp].

@@

We next examined the possibility that ascertainment biases were differentially impacting the inference of evolution following duplication and speciation events. We focused on two possible sources of bias - node depth and branch length. We found no evidence that either affected our results (Supplementary materials).

@@

>>>>

Most CFG studies to date compare gene expression across species, often between distinct cells, tissues or developmental time points. Gene expression has been a popular target of CFG studies because, with the advent of RNA-Seq and related transcriptome sequencing methods, it is the most readily collected functional genomics trait across diverse species. Here we reconsider two recent comparative analyses of gene expression data [@KryuchkovaMostacci:2016iw; @Levin:2016bp].

@@

We next examined the possibility that ascertainment biases were differentially impacting the inference of evolution following duplication and speciation events. We focused on two possible sources of bias - node depth and branch length. We found no evidence that either affected our results (Supplementary Materials). We also examined the sensitivity of the results to the calibration times used for speciation events on the gene tree. This is important because it is expected that the most recent common ancestor of two genes that diverge due to speciation is older than the speciation event itself due to incomplete lineage sorting. There is also uncertainty associated with the timing of these speciation events. In replicate analyses we added random noise to the calibration times and found that it does not impact our inability to reject the null hypothesis (Supplementary Materials).

@@

#### Investigation of sensitivity to calibration times

```{r calibration_sensitivity, cache=TRUE, echo=FALSE, fig.cap="XX_PIC_VAR", warning=FALSE, message=FALSE}

	noised_replicate_n = 10
	sd_fraction = 0.2

	noised_dates = 
		replicate( 
			noised_replicate_n, 
			add_noise_calibration_times( calibration_times, sd_fraction ),
			simplify = FALSE
		)

	nodes_contrast_noised_list = lapply(
		noised_dates,
		function( x ){
			gene_trees_pruned %>% 
				calibrate_trees( x, model="correlated" ) %>% 
				add_pics_to_trees() %>% 
				summarize_contrasts()
		}
	)

	p_noised = lapply( nodes_contrast_noised_list, wilcox_oc )

We examined the ensitivity of our results to the specification of calibration dates for the speciation nodes. In `r noised_replicate_n` reanalyses, we drew a new date for each calibration from a normal distribution with the mean of the original date and a standard deviation `r sd_fraction` times the original date. If any daugter nodes became older than their parent, we repeated the sampling until the dates were congruent with the topology. The minimum Wilcoxon p in these reanalyses was `r min( as.numeric( unlist( p_noised ) ) )`, *i.e.* none of them reject the null hypothesis that the rate of evolution of Tau is greater following duplication events than speciation events. This is consistent with the analysis that uses the calibration dates as specified, indicating that our results are robust to the selection of calibration times for speciation nodes.
